%!TEX root = nonabelions.tex

% Consider biblatex \usepackage[sorting=none,firstinits=true]{biblatex}

\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{99}
\bibitem{ainsworth slingerland} R. Ainsworth, J. Slingerland. \textit{Topological Qubit Design and Leakage.} New J. Phys. 13 065030. \href{https://arxiv.org/abs/1102.5029}{\texttt{arXiv:1102.5029}} (2011)
\bibitem{non-abelian experimental} S. An, P. Jiang, H. Choi, W. Kang, S. Simon, L. Pfeiffer, K. West, K. Baldwin. \textit{Braiding of Abelian and Non-Abelian Anyons in the Fractional Quantum Hall Effect.} \href{https://arxiv.org/abs/1112.3400}{\texttt{arXiv:1112.3400}} (2011)
\bibitem{ballentine} L. Ballentine. \textit{Quantum mechanics: A modern development.} World Scientific (1988)
\bibitem{bonderson} P. Bonderson \textit{Non-Abelian Anyons and Interferometry.} (2007) Ph.D Thesis
\bibitem{braid topologies} N. Bonesteel, L. Hormozi, G. Zikos, and S. Simon. \textit{Braid topologies for quantum computation.} Phys. Rev. Lett. 95 (2005), 140503. arXiv:quant-ph/0505665.
\bibitem{hard-core} M. Bourdeau, R. Sorkin. \textit{When can identical particles collide?} Phys.Rev. D45 (1992) 687-696. \url{http://doi.org/10.1103/PhysRevD.45.687}
\bibitem{abelian fqh} F. Camino, Z. Wei, V. Goldman. \textit{Realization of a Laughlin quasiparticle interferometer: Observation of fractional statistics.} \texttt{arXiv:cond-mat/0502406}. Phys. Rev. B 72, 075342 (2005)
\bibitem{myrheim} A. Comtet, T. Jolicoeur, S. Ouvry, F. David. (Eds.) \textit{Topological aspects of low dimensional systems.} Springer (1999)
\bibitem{dawson nielsen} C. Dawson, M. Nielsen. \textit{The Solovay-Kitaev algorithm.} \href{https://arxiv.org/abs/quant-ph/0505030}{\texttt{arXiv:quant-ph/0505030}} Quantum Information \& Computation archive. Volume 6 Issue 1, (2006) Pages 81-95
\bibitem{dellantonio} G. Dell'Antonio, R. Figari, A. Teta. \textit{Statistics in Space Dimension Two.} Letters in Mathematical Physics 40: 235–256, 1997.
\bibitem{doplicher} S. Doplicher, K. Fredenhagen, J. Roberts. \textit{The quantum structure of spacetime at the planck scale and quantum fields.} Commun. Math. Phys. 172, 187-220 (1995)
\bibitem{dummit foote} D. Dummit, R. Foote. \textit{Abstract algebra.} 3rd edition. Wiley. (2003)
\bibitem{tensor categories} P. Etingof, S. Gelaki, D. Nikshych, V. Ostrik. \textit{Tensor Categories.} AMS \url{http://www-math.mit.edu/~etingof/egnobookfinal.pdf} (2015)
\bibitem{configuration spaces} E. Fadell, L. Neuwirth. \textit{Configuration spaces.} Math. Scand. 10 (1962) 111–118
\bibitem{freedman kitaev larsen wang} M. Freedman, A. Kitaev, M. Larsen and Z. Wang. \textit{Topological quantum computation.} Bull. Am. Math. Soc. 40 (2003), p. 31–38. \\ \url{http://dx.doi.org/10.1090/S0273-0979-02-00964-3}
\bibitem{fröhlich} J. Fröhlich. \textit{Quantum statistics and locality.} Proceedings of the Gibbs symposium, Yale University, May 15-17 (1989)
\bibitem{nonperturbative} J. Fröhlich. \textit{Statistics of Fields, the Yang Baxter Equation and the Theory of Knots and Links.} \textit{Nonperturbative quantum field theory.} Springer US, 1988. 71-100.
\bibitem{hoholt} M. Hoffmann-Ostenhof, T. Hoffmann-Ostenhof, A. Laptev, J. Tidblom. \textit{Many-particle Hardy Inequalities.} J. London Math. Soc. 77 (2008), 99–114.
\bibitem{topological quantum compiling} L. Hormozi, G. Zikos, N. Bonesteel, S. Simon. \textit{Topological quantum compiling.} Phys. Rev. B 75, 165310 (2007), \href{https://arxiv.org/abs/quant-ph/0610111}{\texttt{arXiv:quant-ph/0610111}} \\ \url{http://link.aps.org/doi/10.1103/PhysRevB.75.165310}
\bibitem{kauffman lomonaco} L. Kauffman, S. Lomonaco. \textit{Topological quantum computing and $SU(2)$ braid group representations.} Proc. of SPIE Vol. 6976  69760M-1 (2008)
\bibitem{khare} A. Khare. \textit{Fractional statistics and quantum theory.} 2nd edition. World Scientific (2005)
\bibitem{kitaev} A. Kitaev. \textit{Anyons in an exactly solved model and beyond.} Annals of Physics 321 (2006) 2. (Revised version \href{https://arxiv.org/abs/cond-mat/0506438}{\texttt{arXiv:cond-mat/0506438}}.)% \\\relax (One of the founding papers.)
\bibitem{kitaev fault-tolerant anyons} A. Kitaev. \textit{Fault-tolerant quantum computation by anyons.} \\ \href{https://arxiv.org/abs/quant-ph/9707021}{\texttt{arXiv:quant-ph/9707021}} Annals Phys. 303 (2003) 2-30
\bibitem{asymptotical top compl} V. Kliuchnikov, A. Bocharov, K. Svore. \textit{Asymptotically optimal topological quantum compiling.} \href{https://arxiv.org/abs/1310.4150}{\texttt{arXiv:1310.4150}} Phys. Rev. Lett. 112, 140504 (2014)
\bibitem{feynmann path integrals indistinguishable particles} M. Laidlaw, C. DeWitt. \textit{Feynman functional integrals for systems of indistinguishable particles.} Phys. Rev. D 3 (1971) 1375–1378.
\bibitem{larson-lundholm} S. Larson, D. Lundholm. \textit{Exclusion bounds for extended anyons.} \href{https://arxiv.org/abs/1608.04684}{\texttt{arXiv:1608.04684}}
\bibitem{laughlin} R. Laughlin, Nobel lecture: Fractional quantization, Rev. Mod. Phys. 71, 863 (1999).
\bibitem{leinaas myrheim} J. M. Leinaas, J. Myrheim. \textit{On the theory of identical particles.} Il Nuovo Cimento B 37, 1 (1977)
\bibitem{lundholm-solovej} D. Lundholm, J. Solovej. \textit{Hardy and Lieb-Thirring Inequalities for Anyons.} \href{https://arxiv.org/abs/1108.5129}{\texttt{arXiv:1108.5129}}, \url{https://doi.org/10.1007/s00220-013-1748-4} Commun. Math. Phys. 322, 883-908 (2013)
\bibitem{lundholm-solovejAHP} D. Lundholm, J. Solovej. \textit{Local exclusion and Lieb-Thirring inequalities for intermediate and fractional statistics.} \href{https://arxiv.org/abs/1301.3436}{\texttt{arXiv:1301.3436}} Ann. Henri Poincaré 15 (2014), 1061-1107
\bibitem{many-anyon trial states} D. Lundholm. \textit{Many-anyon trial states.} (2016) \href{https://arxiv.org/abs/1608.05067}{\texttt{arXiv:1608.05067}} To appear in Phys. Rev. A.
\bibitem{methmmp} D. Lundholm. \textit{Methods of modern mathematical physics: Uncertainty and exclusion principles in quantum mechanics.} Lecture notes. \url{https://people.kth.se/~dogge/mp/methmmp.pdf} (2017)
\bibitem{lundholm-rougerie} D. Lundholm, N. Rougerie. \textit{Emergence of Fractional Statistics for Tracer Particles in a Laughlin Liquid.} Phys. Rev. Lett. 116, 170401 (2016)
\bibitem{mac lane} S. Mac Lane. \textit{Categories for the Working Mathematician, 2nd Edition}. Graduate Texts in Mathematics, Springer-Verlag (1998).
\bibitem{mancarella} F. Mancarella, A. Trombetoni. \textit{Statistical Mechanics of an Ideal Gas of Non-Abelian Anyons.} \href{https://arxiv.org/abs/1204.6656}{\texttt{arXiv:1204.6656}} Nuclear Physics, Section B 867 (2013), pp. 950-976
\bibitem{naaijkens} P. Naaijkens. \textit{PhD Thesis: Anyons in Infinite Quantum Systems: QFT in $d=2+1$ and the Toric Code} \url{http://www.math.ru.nl/~landsman/Naaijkens.pdf} (1982) % (Contains an account of the categorical framework for anyons.)
\bibitem{nakahara} M. Nakahara. \textit{Geometry, Topology and Physics.} IOP Publishing. (2003)
\bibitem{nayak} C. Nayak, S. H. Simon, A. Stern, M. Freedman, S. D. Sarma. \textit{Non-Abelian Anyons and Topological Quantum Computation.} \href{https://arxiv.org/pdf/0707.1889.pdf}{\texttt{arXiv:0707.1889}} Rev. Mod. Phys. 80, 1083 (2008).
\bibitem{nielsen chuang} M. Nielsen, I. Chuang. \textit{Quantum computation and quantum information.} Cambridge university press (2010).
\bibitem{feynmann path integral} R. P. Feynman. \textit{Space-time approach to non-relativistic quantum mechanics.} Rev. Mod. Phys. 20 (1948) 367–387.
\bibitem{pachos book} J. Pachos. \textit{Introduction to Topological Quantum Computation.} Cambridge University Press. (2012) \\ \url{http://quantum.leeds.ac.uk/jiannis-pachos/book.html}% \\ \url{http://quantum.leeds.ac.uk/fileadmin/user_upload/Jiannis/IntroTQC.pdf}
\bibitem{prakash} P. Panangaden, E. Paquette \textit{A categorical presentation of quantum computation with anyons.} Volume 813 of the series Lecture Notes in Physics pp 983-1025 (2010) % \url{http://www.cs.mcgill.ca/~prakash/Pubs/MTCanyons.pdf}
\bibitem{polychronakos} A. Polychronakos. \textit{Generalized statistics in one dimension.} (1999) \href{https://arxiv.org/abs/hep-th/9902157}{\texttt{arXiv:hep-th/9902157}} \verb|doi:10.1007/3-540-46637-1_5|
\bibitem{preskill} J. Preskill. \textit{Lecture Notes for Physics 219: Quantum Computation, Chapter 9: Topological quantum computation}. \\ \url{http://www.theory.caltech.edu/~preskill/ph219/topological.pdf} (2004)
\bibitem{reed-simon} M. Reed, B. Simon. \textit{Methods of Modern Mathematical Physics: Functional Analysis.} Academic Press. (1980)
\bibitem{shor fault-tolerant} P. Shor. \textit{Fault-tolerant quantum computation.} \href{https://arxiv.org/abs/quant-ph/9605011}{\texttt{arXiv:quant-ph/9605011}} 37th Symposium on Foundations of Computing, IEEE Computer Society Press, 1996, pp. 56-65
\bibitem{one mobile quasiparticle} S. Simon, N. Bonesteel, M. Freedman, N. Petrovic, L. Hormozi. \textit{Topological Quantum Computing with Only One Mobile Quasiparticle.} \href{https://arxiv.org/abs/quant-ph/0509175}{\texttt{arXiv:quant-ph/0509175}} Phys.Rev.Lett. 96 (2006) 070503
\bibitem{slingerland bais} J. Slingerland, F.A. Bais. \textit{Quantum groups and nonabelian braiding in quantum Hall systems} \href{https://arxiv.org/abs/cond-mat/0104035}{\texttt{arXiv:cond-mat/0104035}} Nucl.Phys. B612 (2001) 229-290
\bibitem{stern} A. Stern. \textit{Anyons and the quantum Hall effect—A pedagogical review.} Annals of Physics 323 (2008) 204–249
\bibitem{strömer} H. Störmer, D. Tsui, and A. Gossard, The fractional quantum Hall effect, Rev. Mod. Phys. 71, S298 (1999).
\bibitem{short intro fib} S. Trebst, M. Troyer, Z. Wang and A. W. W. Ludwig. \textit{A Short Introduction to Fibonacci Anyon Models.} Progress of Theoretical Physics Supplement No. 176, 2008. \\ \url{http://stationq.cnsi.ucsb.edu/~wang/Publications/34.pdf}
\bibitem{tuba} I. Tuba. \textit{Braid Representations and Tensor Categories.} PhD thesis, University of California. (2000)
\bibitem{wang book} Z. Wang. \textit{Topological Quantum Computation.} Microsoft Research Station Q, University of California. AMS and CBMS. (2010)
\bibitem{oskar} O. Weinberger. \textit{The braid group, representations and non-abelian anyons.} Bachelor's thesis, KTH. (2015) \href{urn:nbn:se:kth:diva-167993}{\texttt{urn:nbn:se:kth:diva-167993}}
\bibitem{wick-wightman-wigner} G. Wick, A. Wightman, E. Wigner. \textit{The intrinsic parity of elementary particles.} Phys. Rev. 88, 101-105 (1952) \href{http://dieumsnh.qfb.umich.mx/archivoshistoricosmq/ModernaHist/Wick.pdf}{pdf}.
\bibitem{wilczek} F. Wilczek. \textit{Quantum Mechanics of Fractional-Spin Particles.} Phys. Rev. Lett. 49, (1982) 957–959. \url{https://doi.org/10.1103/PhysRevLett.49.957}
\bibitem{fractional angular momentum} Y. Zhang, G. Sreejith, N. Gemelke, J. Jain. \textit{Fractional Angular Momentum in Cold-Atom Systems.} Phys. Rev. Lett. 113, 160404 (2014)
\end{thebibliography}

% \begin{thebibliography}{99}
% \bibitem{leinaas myrheim} J. Leinaas, J. Myrheim. \textit{On the theory of identical particles.} Il Nuovo Cimento B 37, 1 (1977)
% \bibitem{wilczek} F. Wilczek. \textit{Quantum Mechanics of Fractional-Spin Particles.} Phys. Rev. Lett. 49, (1982) 957–959. \url{https://doi.org/10.1103/PhysRevLett.49.957}
% \bibitem{nakahara} M. Nakahara. \textit{Geometry, Topology and Physics.} IOP Publishing. (2003)
% \bibitem{fröhlich} J. Fröhlich. \textit{Quantum statistics and locality.} Proceedings of the Gibbs symposium, Yale University, May 15-17 (1989)
% \bibitem{lundholm-solovej} D. Lundholm, J. Solovej. \textit{Hardy and Lieb-Thirring Inequalities for Anyons.} \href{https://arxiv.org/abs/1108.5129}{\texttt{arXiv:1108.5129}}, \url{https://doi.org/10.1007/s00220-013-1748-4} Commun. Math. Phys. 322, 883-908 (2013)
% \bibitem{lundholm-solovejAHP} D. Lundholm, J. Solovej. \textit{Local exclusion and Lieb-Thirring inequalities for intermediate and fractional statistics.} \href{https://arxiv.org/abs/1301.3436}{\texttt{arXiv:1301.3436}} Ann. Henri Poincaré 15 (2014), 1061-1107
% \bibitem{hard-core} M. Bourdeau, R. Sorkin. \textit{When can identical particles collide?} Phys.Rev. D45 (1992) 687-696. \url{http://doi.org/10.1103/PhysRevD.45.687}
% \bibitem{mancarella} F. Mancarella, A. Trombetoni. \textit{Statistical Mechanics of an Ideal Gas of Non-Abelian Anyons.} \href{https://arxiv.org/abs/1204.6656}{\texttt{arXiv:1204.6656}} Nuclear Physics, Section B 867 (2013), pp. 950-976
% \bibitem{many-anyon trial states} D. Lundholm. \textit{Many-anyon trial states.} (2016) \href{https://arxiv.org/abs/1608.05067}{\texttt{arXiv:1608.05067}} To appear in Phys. Rev. A.
% \bibitem{methmmp} D. Lundholm. \textit{Methods of modern mathematical physics: Uncertainty and exclusion principles in quantum mechanics.} Lecture notes. \url{https://people.kth.se/~dogge/mp/methmmp.pdf} (2017)
% \bibitem{larson-lundholm} S. Larson, D. Lundholm. \textit{Exclusion bounds for extended anyons.} \href{https://arxiv.org/abs/1608.04684}{\texttt{arXiv:1608.04684}}
% \bibitem{dummit foote} D. Dummit, R. Foote. \textit{Abstract algebra.} 3rd edition. Wiley. (2003)
% \bibitem{laughlin} R. B. Laughlin, Nobel lecture: Fractional quantization, Rev. Mod. Phys. 71, 863 (1999).
% \bibitem{strömer} H. Störmer, D. Tsui, and A. Gossard, The fractional quantum Hall effect, Rev. Mod. Phys. 71, S298 (1999).
% \bibitem{myrheim} A. Comtet, T. Jolicoeur, S. Ouvry, F. David. (Eds.) \textit{Topological aspects of low dimensional systems.} Springer (1999)
% \bibitem{oskar} O. Weinberger. \textit{The braid group, representations and non-abelian anyons.} Bachelor's thesis, KTH. (2015) \href{urn:nbn:se:kth:diva-167993}{\texttt{urn:nbn:se:kth:diva-167993}}
% \bibitem{configuration spaces} E. Fadell, L. Neuwirth. \textit{Configuration spaces.} Math. Scand. 10 (1962) 111–118
% \bibitem{feynmann path integral} R. P. Feynman. \textit{Space-time approach to non-relativistic quantum mechanics.} Rev. Mod. Phys. 20 (1948) 367–387.
% \bibitem{feynmann path integrals indistinguishable particles} M. G. G. Laidlaw, C. M. DeWitt. \textit{Feynman functional integrals for systems of indistinguishable particles.} Phys. Rev. D 3 (1971) 1375–1378.
% \bibitem{polychronakos} A. Polychronakos. \textit{Generalized statistics in one dimension.} (1999) \href{https://arxiv.org/abs/hep-th/9902157}{\texttt{arXiv:hep-th/9902157}} \verb|doi:10.1007/3-540-46637-1_5|
% \bibitem{doplicher} S. Doplicher, K. Fredenhagen, J. Roberts. \textit{The quantum structure of spacetime at the planck scale and quantum fields.} Commun. Math. Phys. 172, 187-220 (1995)
% \bibitem{reed-simon} M. Reed, B. Simon. \textit{Methods of Modern Mathematical Physics: Functional Analysis.} Academic Press. (1980)
% \bibitem{wick-wightman-wigner} G. Wick, A. Wightman, E. Wigner. \textit{The intrinsic parity of elementary particles.} Phys. Rev. 88, 101-105 (1952) \href{http://dieumsnh.qfb.umich.mx/archivoshistoricosmq/ModernaHist/Wick.pdf}{pdf}.
% \bibitem{hoholt} M. Hoffmann-Ostenhof, T. Hoffmann-Ostenhof, A. Laptev, J. Tidblom. \textit{Many-particle Hardy Inequalities.} J. London Math. Soc. 77 (2008), 99–114.
% \bibitem{nonperturbative} J. Fröhlich. \textit{Statistics of Fields, the Yang Baxter Equation and the Theory of Knots and Links.} \textit{Nonperturbative quantum field theory.} Springer US, 1988. 71-100.
% \bibitem{stern} A. Stern. \textit{Anyons and the quantum Hall effect—A pedagogical review.} Annals of Physics 323 (2008) 204–249
% \bibitem{dellantonio} G. Dell'Antonio, R. Figari, A. Teta. \textit{Statistics in Space Dimension Two.} Letters in Mathematical Physics 40: 235–256, 1997.
% \bibitem{kitaev} A. Kitaev. \textit{Anyons in an exactly solved model and beyond.} Annals of Physics 321 (2006) 2. (Revised version \href{https://arxiv.org/abs/cond-mat/0506438}{\texttt{arXiv:cond-mat/0506438}}.)% \\\relax (One of the founding papers.)
% \bibitem{preskill} J. Preskill. \textit{Lecture Notes for Physics 219: Quantum Computation, Chapter 9: Topological quantum computation}. \\ \url{http://www.theory.caltech.edu/~preskill/ph219/topological.pdf} (2004)
% \bibitem{bonderson} P. Bonderson \textit{Non-Abelian Anyons and Interferometry.} (2007) Ph.D Thesis
% \bibitem{short intro fib} S. Trebst, M. Troyer, Z. Wang and A. W. W. Ludwig. \textit{A Short Introduction to Fibonacci Anyon Models.} Progress of Theoretical Physics Supplement No. 176, 2008. \\ \url{http://stationq.cnsi.ucsb.edu/~wang/Publications/34.pdf}
% \bibitem{lundholm-rougerie} D. Lundholm, N. Rougerie. \textit{Emergence of Fractional Statistics for Tracer Particles in a Laughlin Liquid.} Phys. Rev. Lett. 116, 170401 (2016)
% \bibitem{abelian fqh} F. Camino, Z. Wei, V. Goldman. \textit{Realization of a Laughlin quasiparticle interferometer: Observation of fractional statistics.} \texttt{arXiv:cond-mat/0502406}. Phys. Rev. B 72, 075342 (2005)
% \bibitem{fractional angular momentum} Y. Zhang, G. Sreejith, N. Gemelke, J. Jain. \textit{Fractional Angular Momentum in Cold-Atom Systems.} Phys. Rev. Lett. 113, 160404 (2014)
% \bibitem{non-abelian experimental} S. An, P. Jiang, H. Choi, W. Kang, S. Simon, L. Pfeiffer, K. West, K. Baldwin. \textit{Braiding of Abelian and Non-Abelian Anyons in the Fractional Quantum Hall Effect.} \href{https://arxiv.org/abs/1112.3400}{\texttt{arXiv:1112.3400}} (2011)
% \bibitem{mac lane} S. Mac Lane. \textit{Categories for the Working Mathematician, 2nd Edition}. Graduate Texts in Mathematics, Springer-Verlag (1998).
% \bibitem{tuba} I. Tuba. \textit{Braid Representations and Tensor Categories.} PhD thesis, University of California. (2000)
% \bibitem{naaijkens} P. Naaijkens. \textit{PhD Thesis: Anyons in Infinite Quantum Systems: QFT in $d=2+1$ and the Toric Code} \url{http://www.math.ru.nl/~landsman/Naaijkens.pdf} (1982) % (Contains an account of the categorical framework for anyons.)
% \bibitem{prakash} P. Panangaden, E. Paquette \textit{A categorical presentation of quantum computation with anyons.} Volume 813 of the series Lecture Notes in Physics pp 983-1025 (2010) % \url{http://www.cs.mcgill.ca/~prakash/Pubs/MTCanyons.pdf}
% \bibitem{tensor categories} P. Etingof, S. Gelaki, D. Nikshych, V. Ostrik. \textit{Tensor Categories.} AMS \url{http://www-math.mit.edu/~etingof/egnobookfinal.pdf} (2015)
% \bibitem{nayak} C. Nayak, S. H. Simon, A. Stern, M. Freedman, S. D. Sarma. \textit{Non-Abelian Anyons and Topological Quantum Computation.} \href{https://arxiv.org/pdf/0707.1889.pdf}{\texttt{arXiv:0707.1889}} Rev. Mod. Phys. 80, 1083 (2008).
% \bibitem{topological quantum compiling} L. Hormozi, G. Zikos, N. Bonesteel, S. Simon. \textit{Topological quantum compiling.} Phys. Rev. B 75, 165310 (2007), \href{https://arxiv.org/abs/quant-ph/0610111}{\texttt{arXiv:quant-ph/0610111}} \\ \url{http://link.aps.org/doi/10.1103/PhysRevB.75.165310}
% \bibitem{wang book} Z. Wang. \textit{Topological Quantum Computation.} Microsoft Research Station Q, University of California. AMS and CBMS. (2010)
% \bibitem{pachos book} J. Pachos. \textit{Introduction to Topological Quantum Computation.} Cambridge University Press. (2012) \\ \url{http://quantum.leeds.ac.uk/jiannis-pachos/book.html}% \\ \url{http://quantum.leeds.ac.uk/fileadmin/user_upload/Jiannis/IntroTQC.pdf}
% \bibitem{ainsworth slingerland} R. Ainsworth, J. Slingerland. \textit{Topological Qubit Design and Leakage.} New J. Phys. 13 065030. \href{https://arxiv.org/abs/1102.5029}{\texttt{arXiv:1102.5029}} (2011)
% \bibitem{one mobile quasiparticle} S. Simon, N. Bonesteel, M. Freedman, N. Petrovic, L. Hormozi. \textit{Topological Quantum Computing with Only One Mobile Quasiparticle.} \href{https://arxiv.org/abs/quant-ph/0509175}{\texttt{arXiv:quant-ph/0509175}} Phys.Rev.Lett. 96 (2006) 070503
% \bibitem{nielsen chuang} M. Nielsen, I. Chuang. \textit{Quantum computation and quantum information.} Cambridge university press (2010).
% \bibitem{dawson nielsen} C. Dawson, M. Nielsen. \textit{The Solovay-Kitaev algorithm.} \href{https://arxiv.org/abs/quant-ph/0505030}{\texttt{arXiv:quant-ph/0505030}} Quantum Information \& Computation archive. Volume 6 Issue 1, (2006) Pages 81-95
% \bibitem{braid topologies} N. Bonesteel, L. Hormozi, G. Zikos, and S. Simon. \textit{Braid topologies for quantum computation.} Phys. Rev. Lett. 95 (2005), 140503. arXiv:quant-ph/0505665.
% \bibitem{freedman kitaev larsen wang} M. Freedman, A. Kitaev, M. Larsen and Z. Wang. \textit{Topological quantum computation.} Bull. Am. Math. Soc. 40 (2003), p. 31–38. \\ \url{http://dx.doi.org/10.1090/S0273-0979-02-00964-3}
% \bibitem{kitaev fault-tolerant anyons} A. Kitaev. \textit{Fault-tolerant quantum computation by anyons.} \\ \href{https://arxiv.org/abs/quant-ph/9707021}{\texttt{arXiv:quant-ph/9707021}} Annals Phys. 303 (2003) 2-30
% \bibitem{shor fault-tolerant} P. Shor. \textit{Fault-tolerant quantum computation.} \href{https://arxiv.org/abs/quant-ph/9605011}{\texttt{arXiv:quant-ph/9605011}} 37th Symposium on Foundations of Computing, IEEE Computer Society Press, 1996, pp. 56-65
% \bibitem{kauffman lomonaco} L. H. Kauffman, S. J. Lomonaco. \textit{Topological quantum computing and $SU(2)$ braid group representations.} Proc. of SPIE Vol. 6976  69760M-1 (2008)
% \bibitem{khare} A. Khare. \textit{Fractional statistics and quantum theory.} 2nd edition. World Scientific (2005)
% \bibitem{ballentine} L. Ballentine. \textit{Quantum mechanics: A modern development.} World Scientific (1988)
% \bibitem{slingerland bais} J. Slingerland, F.A. Bais. \textit{Quantum groups and nonabelian braiding in quantum Hall systems} \href{https://arxiv.org/abs/cond-mat/0104035}{\texttt{arXiv:cond-mat/0104035}} Nucl.Phys. B612 (2001) 229-290
% \bibitem{asymptotical top compl} V. Kliuchnikov, A. Bocharov, K. Svore. \textit{Asymptotically optimal topological quantum compiling.} \href{https://arxiv.org/abs/1310.4150}{\texttt{arXiv:1310.4150}} Phys. Rev. Lett. 112, 140504 (2014)
% \end{thebibliography}
